**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-05-25 submission/manuscript.Rmd
discussion

We identified a range of Simpson diversity values between patients and between each anatomical site. As this measurement takes both number of species and abundance of species into account, it seems that there is a varied level of each component along the human colon. There was no clear pattern of diversity when comparing patients- some patients had a higher level of diversity in the proximal than the distal, some patients had the opposite. An early study of microbial diversity and membership of three human subjects found a varied level of diversity in each subject, but that subjects were overall more similar to themselves than to each other (Eckberg 2005). We next used the thetaYC dissimilarity metric to compare the communities present at each anatomical location to each other. We found that while there was a wide range of similarity of each site within a person, the study participants were ultimately more similar to themselves than all of the other participants. This finding is consistent with numerous studies examining the biogeography of the colon in healthy humans (Eckberg 2005, Aguierre de Carcer, 2015).

@@

other factors besides oxygen? pH? 
offer another model/schematic?
some of the very high OTUs BLAST to stool residents, like that one bacteriodes (OTU20) - not necessarily anything interesting there.

>>>>

Discussion of the phyla present and at what levels? Good refs in the gut biogeography paper - mucosa vs lumen enrichment stuff "significant variability between sample locations less than 1 cm apart, which suggests that mucosal microbial populations occur in patches" there is also patchiness in fecal samples themselves: spatial niche partitioning in faeces. . Patchiness/sampling an issue as well as differences in human age, sex, genotype, adn definitely diet, pH, oxygen, etc. (does this go in the intro?)

We identified a range of Simpson diversity values between patients and between each anatomical site. As this measurement takes both number of species and abundance of species into account, it seems that there is a varied level of each component along the human colon. There was no clear pattern of diversity when comparing patients- some patients had a higher level of diversity in the proximal than the distal colon, some patients had the opposite. An early study of microbial diversity and membership of three human subjects found a varied level of diversity in each subject, but that subjects were overall more similar to themselves than to each other (Eckberg 2005). We next used the thetaYC dissimilarity metric to compare the communities present at each anatomical location to each other. We found that while there was a wide range of similarity of each site within a person, the study participants were ultimately more similar to themselves than all of the other participants. This finding is consistent with numerous studies examining the biogeography of the colon in healthy humans (Eckberg 2005, Aguierre de Carcer, 2015, Zhang et al 2013).

@@

offer another model/schematic?
some of the very high OTUs BLAST to stool residents, like that one bacteriodes (OTU20) - not necessarily anything interesting there.
